\documentclass{article}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{soul}
\title{SE 3XA3: Problem Statement\\ PineSweeper}
\author{Team 07; PineApple
		\\ Student 1: Prince Sandhu; sandhps2
		\\ Student 2: Varun Singh Rathore; rathorvs
		\\ Student 3: Vishesh Gulatee; gulatev
}
\date{September 29, 2016}
\begin{document}
\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
22/09/2016 & Prince Sandhu, Varun Rathore, Vishesh Gulatee & Initial Draft\\
29/09/2016 & Prince Sandhu, Varun Rathore, Vishesh Gulatee & Conversion to LaTeX\\
03/12/2016 & Prince Sandhu, Varun Rathore, Vishesh Gulatee & Revision 1\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}
\newpage
\maketitle

\vspace{5mm}
Although it is customarily normal, boredom is an exceedingly frequent feeling which causes people to feel unsatisfied and uninterested,
which in turn can affect their productivity. This is fundamental issue that the application aims to solve; it provides users with a means to
engage and entertain themselves, while also challenging their mental faculties. \vspace{5mm}

The stakeholders of the application include the individuals of all ages who enjoy fun and simple games that are intuitive. Another exemplar
of a stakeholder of the application is the developers of the game. Not only do the developers play a significant role in designing the
application, they also have to adhere to various license agreements. \textcolor{red}{Lastly, Dr. Spencer Smith, SFWR ENG 3XA3 teaching
assistants, and fellow colleague testers are classified as another category of stakeholders, as they are responsible for evaluating the project.
By taking the relevant steps to document and test the project \textit{PineSweeper} certifies that open-source developers can efficiently 
maintain and improve the design in the future.} \vspace{5mm}

Regarding the environment of the software, PineSweeper is to be built in Java and it must run on both, the Windows and Mac operating
systems. In addition to the aforementioned, the application does not need any special hardware requirements. The setting in which the
game is to be played in, such as retail or hospitals, is insignificant, as PineSweeper will be designed to run on both desktops and laptops.


\end{document}